Automated Lensing Learner - I: An automated Strong Lensing Identification Pipeline

### 2017-03-23 ms.tex
Fixed minor em bugs and table alignment issue

\begin{table}
\caption{Grid Search of Pipeline Parameters}
\begin{center}
\begin{tabular}{cccccc}
\hline \\ [-0.2cm]
N$_{orient}$ & Pixels/Cell & Cells/Block & C$_{reg}$ & Score \\ [0.2cm]
\hline \\ [-0.2cm]
\multicolumn{6}{c}{(a) HST-like data} \\ [0.2cm]
\hline \\ [-0.2cm]
9 & (16, 16) & (4, 4) & 10. & $0.90141\pm 0.00658$ \\ [0.2cm]
9 & (24, 24) & (3, 3) & 10. & $0.89266\pm 0.01033$ \\ [0.2cm]
9 & (16, 16) & (1, 1) & 10. & $0.87484\pm 0.00671$ \\ [0.2cm]
7 & (16, 16) & (4, 4) & 10. & $0.90031\pm 0.00956$ \\ [0.2cm]
5 & (16, 16) & (4, 4) & 10. & $0.89453\pm 0.00840$ \\ [0.2cm]
9 & (32, 32) & (4, 4) & 10. & $0.85828\pm 0.01004$ \\ [0.2cm]
9 & (32, 32) & (4, 4) & 50. & $0.87344\pm 0.01267$ \\ [0.2cm]
\hline \\ [-0.2cm]
\multicolumn{6}{c}{(b) LSST-like data} \\ [0.2cm]
\hline \\ [-0.2cm]
3 & (5, 5) & (4, 4) & 100. & $0.64328\pm 0.00769$ \\ [0.2cm]
4 & (5, 5) & (4, 4) & 100. & $0.62469\pm 0.00485$ \\ [0.2cm]
3 & (5, 5) & (2, 2) & 100. & $0.63281\pm 0.00869$ \\ [0.2cm]
5 & (5, 5) & (4, 4) & 100. & $0.62734\pm 0.00800$ \\ [0.2cm]
3 & (3, 3) & (4, 4) & 100. & $0.59109\pm 0.00313$ \\ [0.2cm]
3 & (3, 3) & (2, 2) & 100. & $0.57297\pm 0.00508$ \\ [0.2cm]
4 & (4, 4) & (3, 3) & 100. & $0.63125\pm 0.01227$ \\ [0.2cm]
\hline
\end{tabular}
\end{center}
\label{tab:gridsearch}
\tablecomments{Panel (a) shows a subsample of the results of a grid
  search for HST across a range of HOG parameters and regression
  coefficient. Panel (b) shows a subsample of the results of a grid
  search for LSST10. Each use a data set of size $2\times8000$ for
  cross validation to get the average scores and standard deviation.
  We explore different HOG parameters in each dataset due to
  resolution and image size differences.}
\end{table}

@@

%-------------------------------------------------%
\subsubsection{Machine Learning Algorithm: Logistic Regression}\label{sec:LR}
%-------------------------------------------------%
The problem of detecting gravitational lenses in images falls under
the general category of {\em{classification}} in machine learning. In
general, the task is to find a function that assigns data points $x$ to
one of two or more classes, denoted by the class label $y$.  This is
equivalent to specifying a decision boundary, or decision boundaries
between the classes in the space of the data points.  (Compare this to
{\em{regression}} in which the task is to find a function $y=f(x)$,
where $y$ is a continuous, rather than discrete, variable.) In our
case, we have two classes: lens and non-lens containing images, and
the data points $x$ are the HOG feature vectors extracted from the
images.  In this paper we use the \em{Logisitic Regression}
(LR) algorithm, for which the decision boundary is a hyperplane.  (The
equivalent in the regression setting would be linear regression.) In
LR we determine the optimal hyperplane by minimizing the objective
function
\begin{equation}
\label{eqn:log_reg_objective}
L(A,b) = \sum_i \log \left[1 + \exp \left(-y_i (A \cdot x_i + b) \right) \right]
\end{equation}
where $x_i$ is a data point (HOG feature vector), $y_i$ is the
known label for that data point ($1$ for a lens containing
image, $-1$ for a non-lens containing), and $A$ and $b$ are
the parameters of the hyperplane. Eq. \ref{eqn:log_reg_objective}
is to be minimized with respect to $A$ and $b$.
Other more complicated machine learning algorithms exist which
do not necessarily produce a linear decision boundary, such as
\em{Support Vector Machines} (SVM), \em{Random Forests}, and
\em{Neural Networks} \citep{hastie_09}.

>>>>

\begin{table}
\caption{Grid Search of Pipeline Parameters}
\begin{center}
\begin{tabular}{cccccc}
\hline \\ [-0.2cm]
N$_{orient}$ & Pixels/Cell & Cells/Block & C$_{reg}$ & Score & \\ [0.2cm]
\hline \\ [-0.2cm]
\multicolumn{6}{c}{(a) HST-like data} \\ [0.2cm]
\hline \\ [-0.2cm]
9 & (16, 16) & (4, 4) & 10. & $0.90141\pm 0.00658$ &\\ [0.2cm]
9 & (24, 24) & (3, 3) & 10. & $0.89266\pm 0.01033$ &\\ [0.2cm]
9 & (16, 16) & (1, 1) & 10. & $0.87484\pm 0.00671$ &\\ [0.2cm]
7 & (16, 16) & (4, 4) & 10. & $0.90031\pm 0.00956$ &\\ [0.2cm]
5 & (16, 16) & (4, 4) & 10. & $0.89453\pm 0.00840$ &\\ [0.2cm]
9 & (32, 32) & (4, 4) & 10. & $0.85828\pm 0.01004$ &\\ [0.2cm]
9 & (32, 32) & (4, 4) & 50. & $0.87344\pm 0.01267$ &\\ [0.2cm]
\hline \\ [-0.2cm]
\multicolumn{6}{c}{(b) LSST-like data} \\ [0.2cm]
\hline \\ [-0.2cm]
3 & (5, 5) & (4, 4) & 100. & $0.64328\pm 0.00769$ &\\ [0.2cm]
4 & (5, 5) & (4, 4) & 100. & $0.62469\pm 0.00485$ &\\ [0.2cm]
3 & (5, 5) & (2, 2) & 100. & $0.63281\pm 0.00869$ &\\ [0.2cm]
5 & (5, 5) & (4, 4) & 100. & $0.62734\pm 0.00800$ &\\ [0.2cm]
3 & (3, 3) & (4, 4) & 100. & $0.59109\pm 0.00313$ &\\ [0.2cm]
3 & (3, 3) & (2, 2) & 100. & $0.57297\pm 0.00508$ &\\ [0.2cm]
4 & (4, 4) & (3, 3) & 100. & $0.63125\pm 0.01227$ &\\ [0.2cm]
\hline
\end{tabular}
\end{center}
\label{tab:gridsearch}

\tablecomments{Panel (a) shows a subsample of the results of a grid
  search for HST across a range of HOG parameters and regression
  coefficient. Panel (b) shows a subsample of the results of a grid
  search for LSST10. Each use a data set of size $2\times8000$ for
  cross validation to get the average scores and standard deviation.
  We explore different HOG parameters in each dataset due to
  resolution and image size differences.}
\end{table}

@@

%-------------------------------------------------%
\subsubsection{Machine Learning Algorithm: Logistic Regression}\label{sec:LR}
%-------------------------------------------------%
The problem of detecting gravitational lenses in images falls under
the general category of {\em{classification}} in machine learning. In
general, the task is to find a function that assigns data points $x$ to
one of two or more classes, denoted by the class label $y$.  This is
equivalent to specifying a decision boundary, or decision boundaries
between the classes in the space of the data points.  (Compare this to
{\em{regression}} in which the task is to find a function $y=f(x)$,
where $y$ is a continuous, rather than discrete, variable.) In our
case, we have two classes: lens and non-lens containing images, and
the data points $x$ are the HOG feature vectors extracted from the
images.  In this paper we use the {\em Logisitic Regression}
(LR) algorithm, for which the decision boundary is a hyperplane.  (The
equivalent in the regression setting would be linear regression.) In
LR we determine the optimal hyperplane by minimizing the objective
function
\begin{equation}
\label{eqn:log_reg_objective}
L(A,b) = \sum_i \log \left[1 + \exp \left(-y_i (A \cdot x_i + b) \right) \right]
\end{equation}
where $x_i$ is a data point (HOG feature vector), $y_i$ is the
known label for that data point ($1$ for a lens containing
image, $-1$ for a non-lens containing), and $A$ and $b$ are
the parameters of the hyperplane. Eq. \ref{eqn:log_reg_objective}
is to be minimized with respect to $A$ and $b$.
Other more complicated machine learning algorithms exist which
do not necessarily produce a linear decision boundary, such as
{\em Support Vector Machines} (SVM), {\em Random Forests}, and
{\em Neural Networks} \citep{hastie_09}.
